Can money buy happiness?

### 2022-04-29 draft2.Rmd
Concluding Thoughts

Can money buy happiness? Our key findings from this project are ______________. We sought to tell a story about the connection between economic prosperity and happiness but with the added factor of working hours. Money is inextricable from the work needed to obtain it, and to base our argument purely on GDP or how much money is possessed completely ignores a key factor: how much are people working to obtain said money. Thus, we tied the two together, factoring in that having more money likely ______ and working fewer hours means that people will _____________. This presents a paradox of sorts, more work generally means more money, and more money means more happiness, but less work also generates more happiness. So where is a harmonious balance found? We see that ________. Our research cannot possibly cover all factors such as access to community programs, optimal living conditions, or types of government and the length to which they go to provide resources. All of these ancillary factors play a role in happiness and the ability to work fewer hours, but we posit that looking purely at money and work can still produce illuminating discoveries.

>>>>

Can money buy happiness? We sought to tell a story about the connection between economic prosperity and quality of life (most specifically happiness) while keeping in mind the added factor of working hours. We found that there is a loose inverse relationship between GDPPC and hours worked, which may highlight differences in technological processes between more and less developed countries. GDPPC does not serve as a perfect measure of the prosperity of a country’s people because it is skewed by income inequality and wealth distribution. GDPPC gives a near-sighted view of the standard of living in any given country, and it should not be used alone to measure something as qualitative as wellness (or happiness). Stressors and work hours are components that are not factored into GDPPC, and higher GDPPC does not even correlate with a greater amount of hours worked. This presents a paradox of sorts, it is commonly thought that more work generally means higher income, and higher income leads to more happiness. We can infer that less time spent working means increased leisure time which can be spent improving overall health and emotional well-being. We also can infer that a certain level of material well-being is necessary because it provides greater access to resources which in turn can boost happiness.  Economic prosperity and holistic well-being have a reciprocal relationship. Our research cannot possibly cover all factors such as access to community programs, optimal living conditions, or types of government and the length to which they go to provide resources. All of these ancillary factors play a role in happiness and the ability to work fewer hours, but we posit that looking purely at income and hours worked can still produce illuminating discoveries and ideas
